Self Regulation Ontology Retest Analyses

### 2018-03-21 code/SRO_Retest_Analyses.Rmd
refactoring

`Plot differences for the measures with differences as examples`

@@

@@

### Conceptual replications 
- Larger reliability estimates for surveys
- Larger variance in reliability estimates for tasks

### Sample size effects/publication bias

Deviance between our mean estimate and the reliability from the literature decreases exponentially with sample size. The smaller the sample size in the literature the more the reliability estimate differs from our results.

```{r}
rel_comp = rel_comp %>%
  mutate(diff_sq = abs(mean_icc - retest_reliability)^2)

rel_comp %>%
  ggplot(aes(sample_size,diff_sq, color=task))+
  # geom_point()+
  #exponential decay (linearized by taking logs of both sides)
  geom_smooth(method="glm",se=FALSE, method.args=list(family=gaussian(link="log")))+
  theme_bw()
```

```{r}
lit_review %>%
  ggplot(aes(sample_size, retest_reliability, color=task))+
  geom_smooth(method='lm')

mod1 = lmer(retest_reliability~sample_size+(1|dv), data=lit_review)

```{r}
#sd by average sample size
lit_review %>%
  group_by(dv) %>%
  summarise(sd_rel = sd(retest_reliability),
            avg_sample_size = mean(sample_size)) %>%
  ggplot(aes(avg_sample_size, sd_rel))+
  geom_point()+
  xlim(0,200)
```

@@

```{r}
with(rel_comp %>% filter(task == "task"), cor(mean_icc, mean_reliability))
```

```{r}
with(rel_comp %>% filter(task == "survey"), cor(mean_icc, mean_reliability))
```

@@

```{r}
mod1 = lmer(retest_reliability ~ mean_icc + (1|dv), data=rel_comp)
mod2 = lmer(retest_reliability ~ mean_icc + (mean_icc|dv), data=rel_comp)

@@

```{r}
mod3 = lmer(retest_reliability ~ mean_icc + scale(sample_size) + (mean_icc|dv), data=rel_comp)

```{r}
mod4 = lmer(retest_reliability ~ mean_icc + scale(days) + scale(sample_size) + (mean_icc|dv), data=rel_comp)

anova(mod3, mod4)
```

Selected model: fixed effect for mean icc and sample size of study, random slope with respect to mean icc and random intercept for each measure

What does it say?

```{r}
summary(mod3)
```

How well does the model fit? (squared correlation between predictions of model and data)

```{r}
cor(predict(mod3), rel_comp$retest_reliability)^2
```

Same result if you do flat model without random slopes for dv's

```{r}
summary(lm(retest_reliability ~ mean_icc+scale(sample_size), data=rel_comp))
```

Visualize hierarchical model:
How would I show random intercepts/slopes? Does the fact that I can't think of how means that there is something wrong with the model?

```{r}
rel_comp %>%
  ggplot()+  
  geom_boxplot(aes(mean_icc, retest_reliability, group=dv))+
  geom_smooth(aes(mean_icc, retest_reliability), method= 'lm')+
  theme_bw()+
  theme(legend.position = 'none')+
  geom_abline(slope=1, intercept=0)+
  # geom_abline(slope=0, intercept=0.3, linetype='dashed')+
  xlim(-0.2, 1)+
  ylim(-0.2, 1)+
  facet_grid(task~.)+
  xlab('Mean bootstrapped ICC')+
  ylab('Reliability estimate from literature')

@@

Potential problems in this graph: 
- not all metrics are ICC's
- difference in delay between completion of two tests (does it make a difference in the lit review?)

>>>>

`Plot difference score distributions for the measures with significant differences as examples`

```{r}
t1_2_difference %>% 
  filter(dv == sig_days_effect$dv[1]) %>%
  mutate(days_btw = as.numeric(days_btw),
         days_bins = ifelse(days_btw < quantile(days_btw, probs=0.33), "short", 
                                                ifelse(days_btw>quantile(days_btw, probs=0.66), "large", "medium"))) %>%
  ggplot(aes(factor(days_bins, levels = c("short", "medium", "large")), difference))+
  geom_boxplot()+
  xlab('delay between two measurements')
```

```{r}
t1_2_difference %>% 
  filter(dv == sig_days_effect$dv[4]) %>%
  mutate(days_btw = as.numeric(days_btw),
         days_bins = ifelse(days_btw < quantile(days_btw, probs=0.33), "short", 
                                                ifelse(days_btw>quantile(days_btw, probs=0.66), "large", "medium"))) %>%
  ggplot(aes(factor(days_bins, levels = c("short", "medium", "large")), difference))+
  geom_boxplot()+
  xlab('delay between two measurements')
```

@@

The literature has smaller sized samples for task measures compared to survey measures that report retest reliability.

```{r}
summary(lm(sample_size ~ task,rel_comp))
```

@@

```{r}
rel_comp = rel_comp %>%
  mutate(retest_reliability_ft = 0.5*log((1+retest_reliability)/(1-retest_reliability))) %>%
  filter(is.finite(retest_reliability_ft)==TRUE)

m1 = rel_comp %>% filter(task == "task") %>% summarise(m1 = mean(retest_reliability_ft))
m2 = rel_comp %>% filter(task == "survey") %>% summarise(m2 = mean(retest_reliability_ft))
n1 = nrow(rel_comp %>% filter(task == "task"))
n2 = nrow(rel_comp %>% filter(task == "survey"))
var1 = rel_comp %>% filter(task == "task") %>% summarise(var1 = var(retest_reliability_ft))
var2 = rel_comp %>% filter(task == "survey") %>% summarise(var1 = var(retest_reliability_ft))
sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
d_lit = abs(m1-m2)/sd_pooled
d_lit
```

`Add column for turk vs lab study`

The literature review conceptually replicates our finding of lower reliability estimates for task measures but with a much smaller effect size (for Fisher transformed reliability estimates).

```{r}
n_df = rel_comp %>% 
  group_by(dv) %>%
  tally()

boot_comp = data.frame()

for(i in 1:length(unique(rel_comp$dv)) ){
  cur_dv = unique(rel_comp$dv)[i]
  n = n_df$n[n_df$dv == cur_dv]
  sample_df = boot_df %>% filter(dv == cur_dv)
  tmp = sample_n(sample_df, n)
  boot_comp = rbind(boot_comp, tmp)
}

rm(cur_dv, n, sample_df, tmp)

boot_comp = boot_comp %>%
  mutate(task=ifelse(grepl("survey", dv), "task", "survey"),
         icc_ft = 0.5*log((1+icc)/(1-icc)))

m1 = boot_comp %>% filter(task == "task") %>% summarise(m1 = mean(icc_ft))
m2 = boot_comp %>% filter(task == "survey") %>% summarise(m2 = mean(icc_ft))
n1 = nrow(boot_comp %>% filter(task == "task"))
n2 = nrow(boot_comp %>% filter(task == "survey"))
var1 = boot_comp %>% filter(task == "task") %>% summarise(var1 = var(icc_ft))
var2 = boot_comp %>% filter(task == "survey") %>% summarise(var1 = var(icc_ft))
sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
d_boot = abs(m1-m2)/sd_pooled
d_boot
```

Square difference between our mean estimate and the reliability from the literature decreases exponentially with sample size. The smaller the sample size in the literature the more the reliability estimate differs from our results.

This plot (weakly) supports that point that our results diverge most from studies with smaller sample sizes.

```{r}
rel_comp = rel_comp %>%
  mutate(diff_sq = abs(mean_icc - retest_reliability))

rel_comp %>%
  ggplot(aes(sample_size,diff_sq, color=task))+
  geom_point()+
  #exponential decay (linearized by taking logs of both sides)
  geom_smooth(method="glm",se=FALSE, method.args=list(family=gaussian(link="log")))+
  theme_bw()+
  theme(legend.title = element_blank())
```

But as the plot suggests these are not significant effects overall.

```{r}
summary(lmer(diff_sq ~ sample_size*task + (1|dv), rel_comp))
```

@@

```{r}
with(rel_comp %>% filter(task == "task"), cor(mean_icc, retest_reliability, method="spearman"))
```

```{r}
with(rel_comp %>% filter(task == "survey"), cor(mean_icc, retest_reliability, method="spearman"))
```

@@

sample one row per measure out of lit review
r^2 of retest_reliability ~ sampled_reliability vs. 
r^2 of retest_reliability ~ mean_icc

coef of retest_reliability ~ sampled_reliability vs. 
coef of retest_reliability ~ mean_icc

```{r}
tmp  = rel_comp %>% filter(dv == unique(rel_comp$dv)[10])

sample_from_dv <- function(df){
  if(nrow(df)>1){
    row_num = sample(1:nrow(df),1)
    sample_row = df[row_num,]
    df = df[-row_num,]
    df$lit_predictor = sample_row$retest_reliability
  }
  return(df)
}

sample_from_dv(tmp)

sampled_df = rel_comp %>%
  group_by(dv) %>%
  do(sample_from_dv(.))

summary(lm(retest_reliability ~ lit_predictor, data=sampled_df))
summary(lm(retest_reliability ~ mean_icc, data=sampled_df))
```

```{r}
mod1 = lmer(retest_reliability ~ mean_icc + (1|dv), data=rel_comp)
mod1a = lm(retest_reliability ~ mean_icc, data=rel_comp)

cor(predict(mod1), rel_comp$retest_reliability)^2
cor(predict(mod1a), rel_comp$retest_reliability)^2

# mod2 = lmer(retest_reliability ~ mean_icc + (mean_icc|dv), data=rel_comp)

rel_comp %>%
  select(dv, retest_reliability, mean_icc)

summary(mod1a)

summary(lm(retest_reliability ~ mean_icc*scale(sample_size), data=rel_comp))

@@

```{r}
rel_comp %>%
  ggplot()+  
  geom_boxplot(aes(mean_icc, retest_reliability, group=dv))+
  geom_smooth(aes(mean_icc, retest_reliability), method= 'lm')+
  theme_bw()+
  theme(legend.position = 'none')+
  geom_abline(slope=1, intercept=0)+
  geom_abline(slope=0, intercept=0.3, linetype='dashed')+
  xlim(-0.2, 1)+
  ylim(-0.2, 1)+
  # facet_grid(task~.)+
  xlab('Mean bootstrapped ICC')+
  ylab('Reliability estimate from literature')

@@

NOTE: not all metrics are ICC's

```{r echo=FALSE}
rm(tmp, rel_comp, boot_comp, d_boot, d_lit, mod1, mod2, mod3, mod4, n_df, m1, m2, var1, var2, sd_pooled, task, i, n1, n2)
```
